The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-08-06 reviews/2016-07-response-to-reviewers.tex

}

\answer{
Point to:
- work on the substitution models showing that the results are robust
- the rationalization of feature selection
- clarifications of choices, such a single-substitution restriction
- precision/recall analyses for all filters
}

\critique{
2. The conclusions about “contractile” processes seem pretty speculative (as almost all reviewers agreed).   Sure, this might be the theoretical implication of iterating this substitution process, but you do not present any further evidence of this type of contraction towards a fixed point.  I think if you want to make this a major conclusion of the paper there is more work to be done.  Also this idea has been explored, in my view, in a much more sophisticated way in the iterated learning literature (e.g., Kalish, Lewandowsky, Griffiths, Kirby… see my PDF comments for specific references).  You should really check these arguments and papers out because you really have an iterated learning task.
}

\answer{We agree the presentation was too much. \unclear{too much?} Point to:
\itx{
\x the integration of the iterated learning literature in review and general discussion
\x the fact that the constraints of the data don't let us explore chains, so we explained our claims more appropriately
}}

@@

\critique{3. The writing of this paper is of very low quality compared to what is expected at the journal.  I will email separately a very detailed editing of the paper via Adobe Acrobat where I tried to point these problems out.  However, it simply couldn’t be published without a nearly complete re-write or very heavy editing.
}

\answerok{Thank you for this very constructive and extensive feedback. We paid signification attention to the writing style in this new version, and large portions of the document have been rewritten and expanded --- all updates are marked in dark blue.}

@@

%\critique{
%The bottom line is that while I think this is a really interesting idea/question, this is not the best execution of this idea that I could imagine being published in the journal.  My gut reaction is that this paper needs a lot of work, additional analysis, and rewriting before it could be published and therefore should be rejected.  However, because the reviewers are unanimously more positive in their evaluation I will invited a revision for this in the hope that you can make it a pretty significant change and can benefit from the excellent and detailed reviewer comments.
%
%So you understand what is requested:  typically papers which are revised at Cognitive Science are returned with a detailed cover letter responding to each of the reviewer comments in detail, along with pointers to what has changed in the paper.  I would appreciate this type of cover letter if you choose to resubmit because it can help me and the reviewers process what changes you made.
%
%Sincerely,
%Todd Gureckis
%Associate editor
%}
%
%\answer{
%}

\subsection*{Reviewer \#1}

\critique{I think this is an interesting approach and dataset for better understanding how sentences are recalled and how paraphrases are constructed.  However, I think that the experiment design needs to be refined, and the project as a whole needs to be better connected to larger theoretical problems and better grounded within cognitive science.}

\answerok{We have been careful to introduce many more connections to the relevant literature: the introduction has been entirely rewritten and is followed by a more thorough presentation of the related work in cognitive science, while the concluding sections (discussion \& concluding remarks) follow your recommendation of connecting our results with the literature.
}

@@

\critique{
Starting with the grounding, the Introduction talks about theories of "knowledge transmission mechanisms" but doesn't provide examples aside from the quote-copying problem. The theories also don't re-appear in the results discussion, leaving the experimental results stranded and unconnected to any larger domain.  No discussion of sentence recall tasks within psycholinguistics is given - there isn't a huge literature on this, but there are at least a few papers that should inform this work, such as Potter \& Lombardi 1990 "Regeneration in the short-term recall of sentences". No discussion is made about whether and how much the substitutions change the quotes (e.g., is the substituted word a synonym, phonological-neighbor, or something else? - cf. Lauf et al 2013 "Analyzing Variation Patterns in Quotes Over Time"). Lastly, the meaning of the analysis (pg. 17-19) of this process as a dynamical system with "cultural attractors" is not fleshed out - why doesn't this predict that all quotes will eventually, through substitution, converge to the same string? (Does it?) As a result, the conclusion that psycholinguistic factors don't have a big impact on substitution likelihood is interesting but doesn't have clear theoretical repercussions, or any clear meaning outside the very specific problem of quote replication.  This needs to be substantially revised and expanded to make this work useful to the audience at large.
}

\answer{Point to:
- the new discussion of results
- the improved review of literature
- the use of H00 to compare to synonyms, and the small exploration of distances travelled by substitutions on the FA and synonym networks
}

\critique{ The experiment design also has some substantial flaws. First, some crucial factors were not considered - most notably, part of speech. I suspect, for instance, that pronouns and other closed-class words less often substituted than open-class words.  Phonological neighborhood density could also be important, though probably less so.  Second, no analysis was done that included all of the factors in, e.g., a multi-feature regression model.  While the features being considered are not strongly correlated, they are still likely to interact - especially if part-of-speech is added.  Third, the restriction to single-word substitutions introduces some significant confounds.  I'm not convinced that correctly and incorrectly copying a quote should be viewed as separate behaviors.
}

\answerok{
We addressed all these points in the revised version:
\itx{
\x We checked the susceptibility of part-of-speech (POS), \unclear{je n'ai pas bien compris ton: ``showing that the effect (closed/open class words being different) expected is very small at best (closed class words would be stopword-likes in our graph)''  (et c'est très légèrement lié à mon point {\bf (5)} dans l'email) -- est-ce qu'il s'agit de l'effet des stopwords-like (== closed class words, exactement?) sur nos résultats (auquel cas, oui, ça a l'air de ne pas arriver souvent, en même temps on se focalise sur les substitutions) ou bien de la susceptibilité des stopwords-like par rapport aux autres (auquel cas elle semble effectivement très inférieure)}
\x Following this suggestion, we added phonological neighborhood density as a word feature. We show that it forms a subgroup of strongly correlated variables, together with orthographic neighborhood density, and choose the latter as a more natural representative of this subgroup given the task under study.
\x We introduced a multi-feature regression model to estimate variation upon substitution, showing that the magnitude of the variation of a feature is mainly predicted by the value of that very feature, generally with negligible interaction with the other features (see also below and figure 8).
\x We expanded substitution models to account for \emph{two-substitutions} \unclear{explain here what is a ``two-substitution'', maybe?}, which yield the same results as single substitutions. 
(Note: %computation notebooks for all models can be found at https://github.com/wehlutyk/brainscopypaste/tree/master/data/notebooks , and the 
graphs produced for all models may be found at <https://huit.re/aEH77Gc3>, and may be commented further upon request.)
}

%We also examined the effect of part-of-speech (POS): Figure 5 details the results on five POS categories. A Goodman-based multinomial goodness-of-fit shows that POS categories do not capture any significant bias in the selection of substitution targets, which is why we largely keep them outside of our analysis.

\critique{But more importantly, the $\sigma_\phi(f)$ calculation can be misleading under the single-substitution restriction: Consider a toy case where all quotes are two words, and there is a single binary feature $F$. $p(F=1) = 3/4$, and the true substitution probabilities, given the value of F, are $p(S|F=1)=1$, $p(S|F=0)=1/2$.  All the quotes where both words have feature $F=1$ will have two substitutions and be omitted from the dataset, as will half of the quotes with one $F=1$ \& one $F=0$ word.  Half of the quotes with two $F=0$ words will also be omitted for having no substitutions.  Due to these omissions, if you actually generate some test data and calculate the $\sigma_F$ values, the $\sigma_F(1)$ value is correctly estimated as 1, but the $\sigma_F(0)$ value is erroneously estimated as 1/8 (not 1/2), because the $F=0$ words are never substituted in the $F=1/F=0$ pairs, and these are three times more common than the $F=0/F=0$ pairs.  I haven't run more complicated cases, such where the length of the quotes vary, but this leads me to have limited confidence that the estimates in the Figure 4 are appropriate to draw conclusions from. I would want to see either a mathematical analysis with realistic values showing that the error is expected to be small in this data or an expansion to include multiple-substitution examples to avoid this problem.
}

@@

\critique{But more importantly, the $\sigma_\phi(f)$ calculation can be misleading under the single-substitution restriction: Consider a toy case where all quotes are two words, and there is a single binary feature $F$. $p(F=1) = 3/4$, and the true substitution probabilities, given the value of F, are $p(S|F=1)=1$, $p(S|F=0)=1/2$.  All the quotes where both words have feature $F=1$ will have two substitutions and be omitted from the dataset, as will half of the quotes with one $F=1$ \& one $F=0$ word.  Half of the quotes with two $F=0$ words will also be omitted for having no substitutions.  Due to these omissions, if you actually generate some test data and calculate the $\sigma_F$ values, the $\sigma_F(1)$ value is correctly estimated as 1, but the $\sigma_F(0)$ value is erroneously estimated as 1/8 (not 1/2), because the $F=0$ words are never substituted in the $F=1/F=0$ pairs, and these are three times more common than the $F=0/F=0$ pairs.  I haven't run more complicated cases, such where the length of the quotes vary, but this leads me to have limited confidence that the estimates in the Figure 4 are appropriate to draw conclusions from. I would want to see either a mathematical analysis with realistic values showing that the error is expected to be small in this data or an expansion to include multiple-substitution examples to avoid this problem.
}

\answer{This case is indeed valid, if there is such a feature (F=1 here) that:
(a) is extremly frequent,
(b) is extremely substituted,
(c) interacts strongly with another feature so that both are often substituted together.

The combination of (a) and (b) is an anti-pattern in our results (more frequent =less substituted), so we could in theory give a bound to the worst error that could have been committed.
However we extend our substitution models to two-substitutions, and observe that the results do not change.
}

\critique{ Some high-level suggestions:
\itx{
\x more discussion of what dynamical systems are and especially their interpretation in this task before their appearance in the results}
}

\answerok{We clarified the notion of dynamical systems when rewriting the introduction and in the ``Variation'' section (including footnote \#22).}

\critique{\itx{
\x needs a substantive discussion of the results}
}

\answerok{An entirely new ``Discussion'' section is now devoted to this task.}

@@

\critique{\itx{
\x show that the phi value is capturing what it purports to capture
\x and that the factors aren't conflated with length
\x is the single-substitution biasing the data?
\x make sure that the reported measures are interpretable
\x if low-frequency words have 1/3 chance of being chosen as substitution (Fig. 4), what if there are four low-frequency words in a quote?
}
}

\answer{
Point to:
- our control of single-substitution bias
- the change in definition of phi. Indeed it was confusing to present it (and measure it) as a probability (which it was, but an aggregated global one, not an in-sentence one), we now measure it as the strength of a bias.
}

\critique{\itx{
\x improving statements of motivation and grounding within cognitive science
\x what are representation transformation processes?
\x give examples in the introduction
\x show how the quotation test case connects to more general representation transformation?}
}

\answerok{
These points should be addressed by the improved introduction. In particular regarding the last question, the new ``Discussion'' section additionally makes a connection with iterated learning literature.
}

@@

\critique{Some low-level points:\itx{
\x the in vitro/in vivo distinction is unfamiliar and ought to be defined in the text
}
}

\answerok{In light of this potential unfamiliarity, we preferred to entirely avoid referring explicitly to this dichotomy (for instance, we now speak of ``corpus-based utterances'' instead of ``in vivo'').}

\critique{\itx{
\x introducing eight measures and then removing three of them due to collinearity is presentationally confusing}}

\unclear{ah oui que répond-on là? qqch comme ça? je te laisse valider:}
\answerok{We agree that introducing twelve\footnote{In the revised version we have 12 measures, instead of 8 in the initial submission.} measures before eventually keeping six of them could complicate the flow of the section on word-level measures. However, we found it more natural to first propose a comprehensive, literature-based list of candidate features before addressing the quantitative analysis with a reduced yet sufficient set of metrics --- especially now that this section has been significantly expanded. We initially favored this solution over first presenting the final list of candidate features and justifying afterwards that they are anyway correlated with a broader list of traditional variables. (NB: An alternative option could consist in presenting the contents of Figs. 1 and 2 in the same figure, if this could be less confusing.)}

@@

\critique{
\itx
{
\x was there a reason to expect that \# of synonyms and \# of phonemes would interact (Fig. 4)?]
}
}

\answer{
Yes, because of the similar curve shapes they had.
We removed number of phonemes now (in favor of number of letters), and number of synonyms doesn't show any effect of susceptibility on the new, improved measure.
}
\unclear{ne serait-ce pas plutôt la raison suivante?\\Except for word frequency, we observed that synonyms and phonems were the only two word features to exhibit an effect on susceptibility (and q quite similar effect for that matter). We thus reasoned that they were good candidates to look for and illustrate potential joint effects.\\However, the revised version now features a much braoder framework to statistically assess joint effects (see Fig. 8), we think it favorably replaces the previous variable-to-variable correlation check (NB: we also replaced the number of phonemes with the number of letters [which makes more sense in our context, see the end of the ``Word-level features'' subsection], number of letters and synonyms do not seem to interact).}

@@

\answer{\unclear{comment était fait le binning avant, d'ailleurs? j'aurais eu envie de dire "integer-based" mais à la vue de l'ancien PDF ça ne colle pas avec les graphiques, et j'ai l'impression qu'on n'en parlait pas non plus -- auquel cas la réponse devrait aussi faire mention de l'avant, qui était probablement l'objectif de la question du reviewer} 
Binning is now by quantiles (makes more sense for the confidence intervals), but the extended notebooks (https://github.com/wehlutyk/brainscopypaste/tree/master/data/notebooks and https://github.com/wehlutyk/brainscopypaste/tree/master/data/figures/susceptibility.ipynb) also include graphs with the fixed-width bins we presented in the first version.
No multiple crossovers were ever observed.
}

\subsection*{Reviewer \#2}
\critique{This is a review of "How do we copy and paste? The semantic drift of quotations in blogspace." This paper attempts to discover the underlying psycholinguistic variables that is involved in blog authors making mistakes in the copying of quotations across time. Although I think the motivations and goals of this article are interesting and noteworthy, I think the actual analysis needs improvement in a number of areas.

Although I appreciate the brief writeup on intrusions in recall, the article fails to capture the amount of research done on this topic. Going back to Deese (1959; the precursor to modern experimental studies on false memory) and the subjective organization results of Tulving (1962) it has been well known that extra-list intrusions in free recall are often semantic in nature, with the intruding word being very similar in meaning to a studied item. A recent study that reinforces this is one by Zaromb, et al. (2006; JEP:LMC).
}

\answerok{Thank you for these very useful and, indeed, relevant pointers.  We accordingly devoted a significant portion of the literature review to the issue of recall (see the ``Related work'' section).}

@@

I understand that word-word metrics are not easily introduced in the type of analysis that the authors are attempting to do, where the analysis of the contributions of different global psycholinguistic variables are being weighed against each other. I just think that type of analysis is inappropriate here. Since the quotations were selected on the basis of single substitutions, it seems to me that the appropriate level of analysis is what properties of the word that is being substituted is the most predictive of the substitution. I suspect that the combination of frequency and semantic similarity will be by far the most predictive variables, consistent with past results on recall.
}

\answer{
Point to:
- discussion of distance travelled by substitution on FA and synonyms networks
- our data is ill-shaped for the kind of topic modelling suggested (aside from the earlier point that even with experiments in the laboratory, such tools don't predict so well)
}

\critique{Beyond this, I think the authors are missing out on the most interesting aspect of the data that they have collected: how the surrounding context of the quotation used is changing across time. That is, the quote is being propagated, and the prior usage of that quote is likely predictive of how that information is spread. This is likely a dynamical process where multiple news sources are used to construct a new blog post, and being able to analyze this type of information propagation would be a very interesting study. I point to the semantic space models cited (and the work derived from them) as being very useful tools to analyze this type of question.
}

\answer{That would indeed be interesting, but not our goal in the paper.\unclear{``merci vieux mais c'est hors-sujet'' ;) Pourrait-on lui dire plus diplomatiquement:} \textcolor{red}{``This would indeed be a very interesting project and prospect, but the data we collected do not enable the study of the surrounding context (in particular, we do neither know the prior usage nor the way information sources may be used) so that this goal remains beyond the scope of our paper.''}}

@@

\subsection*{Reviewer \#3}
\critique{In this paper, the authors analyze a large data set of quotations taken from a variety of news sources to study the form of substitutions in quotes, to determine if the transformations follow expected patterns given psycholinguistic theory.  Specifically, the words that are likely to be substituted are found to be less frequent words, and the pattern of substitution is such that the substituting word is more frequent, acquired earlier, and has lower clustering in the free-association word network.  These patterns are consistent with expected cognitive biases.

There are a few issues I would want to see addressed.
\bigskip

Foremost is the method of detecting substitution.  I understand that, given the data set, there is no perfect way to identify what quote is a transformation of what quote, and that it is not feasible to test all possible methods AND that it is simpler to focus on one method for the purposes of the paper.  However, given that this decision of which method to use can directly influence the main conclusions, it behooves the authors to do some sort of robustness check around this method.  For example, one could imagine two distinct groups that only exactly copy from themselves and never copy from each other, where one always publishes earlier than the other.  If the earlier-publishing group tended to select variations of quotes that used lower-frequency words, and the later-publishing group tended to select variations of quotes that used higher-frequency words, this method would infer many more low-frequency to high-frequency substitutions than actually existed.  This may not be a likely scenario, but it demonstrates the benefit of a robustness check. Trying the same analysis with one or two different substitution models would strengthen the authors' claims.
}

\answerok{There are indeed very many possible models, yet we agree that a robustness check is also very sensible.  Substitution detection relies on a number of assumptions and we identified four binary parameters that differentiate potential models, such that the resulting 16 combinations cover most of the reasonable answers to inference uncertainties. We thus implemented, tested and checked these models, and we can report that our results remain valid for all 16 models (for the sake of clarity, we do not specifically report on these models, though).  \\

This leads to a much more detailed ``Substitution Model'' subsection which discusses these options along with the reference model we used throughout the paper.
}

@@

\critique{ A second issue is the time spent on feature selection.  It is unclear why the authors do feature selection at all, as "the analysis is done on a per-feature basis."  It would again add to the robustness of their claims if they showed that all of the correlated features show the same pattern of susceptibility and bias in substitution.  In the same vein, it is not clear why the authors claim that age of acquisition, frequency, and number of synonyms have low levels of correlation "excluding the network properties".  Why would one ignore the correlations with the network features?
}

\answer{Point to:
- the improved substitution selection section
- the graphics for the other features, available in the notebooks (https://github.com/wehlutyk/brainscopypaste/tree/master/data/notebooks) and figures (https://github.com/wehlutyk/brainscopypaste/tree/master/data/figures/susceptibility.ipynb), which we can put in a Supplementary Information if needed
}

### 2016-08-06 reviews/2016-07-response-to-reviewers.tex

\critique{
One smaller issue has to do with the filtering of the quotations.  The authors manually inspected the filtered quotes to see how many real event-related utterances are incorrectly filtered, but I would argue the precision of the filter is more important than the recall; how many of the kept quotes are not real event-related utterances?  Why not do manual coding of those and report that accuracy?
}

\answerok{This is an important empirical point which we did not address systematically in the first submission.  We now have done this manual coding step and are glad to be able to report a (satisfying) accuracy in the relevant cases.}

\critique{Finally, while I understand the appeal of doing a dynamic systems analysis to find the convergence points of the substitutions, but it is not really valid here.  The analysis in this paper does not provide information on what happens with multiple substitutions, so the authors cannot really make claims about the convergence points given this methodology.
}

\answerok{In this revised version, we better explained our claims and their limits (see for instance the second paragraph of the ``Discussion'' section, without overstating our findings.}

@@

\critique{Overall, the analysis of the patterns of substitution in a series of quotations to validate psycholinguistic theory is novel and advances the current science.  The results would be more solid with some additional robustness checks, but in general they are quite intuitive.  I hope in the future the authors find a dataset that provides certain information about the transmission of language from one person to another, as this would allow for stronger claims about causality and greater confidence in the pattern of substitutions, as well as a finer-grained analysis of repeated substitutions.
}

\answerok{\textcolor{red}{[C: j'ai ajouté ça, je te laisse confirmer si ce teasing te semble approprié]}\\ On a side note, we entirely agree with the relevance of pursuing this research program in these directions, as the \emph{in vitro} observation of information transmission and its evolution is part of an ongoing project (which nonetheless remains beyond the scope of the current paper).}

### 2016-08-06 brains-conclusion.tex
further cover letter corrections, passing over to Seb

We do not actually observe quotes converging on a global scale towards attractors in their various dimensions.
Indeed the limits of the data set don't allow us to infer chains of substitutions, and substitutions themselves are not the only type of transformation at work in the data set.
Nonetheless, these findings (1) bring light to this simple type of transformation, and (2) are consistent with known psycholinguistic effects, with the hypothesis of cultural attractors in representations from everyday life, and with the lineage specificity discussed in the iterated learning literature~\citep{claidiere_cultural_2014,cornish_systems_2013}.
They are obtained by successfully applying knowledge from cognitive science to real-life complex data, a task that remains a challenge in the study of cultural evolution.
\tb{More broadly,} we believe that applying such data mining tools to manage the complexity of real-life data is a promising approach for the joint analysis of cognitive science and culture.

>>>>

We do not actually observe quotes converging on a global scale towards attractors in their various dimensions.
Indeed the limits of the data set do not allow us to infer chains of substitutions, and substitutions themselves are not the only type of transformation at work in the data set.
Nonetheless, these findings (1) bring light to this simple type of transformation, and (2) are consistent with known psycholinguistic effects, with the hypothesis of cultural attractors in representations from everyday life, and with the lineage specificity discussed in the iterated learning literature~\citep{claidiere_cultural_2014,cornish_systems_2013}.
They are obtained by successfully applying knowledge from cognitive science to real-life complex data, a task that remains a challenge in the study of cultural evolution.
\tb{More broadly,} we believe that applying such data mining tools to manage the complexity of real-life data is a promising approach for the joint analysis of cognitive science and culture.

### 2016-08-06 brains-protocol.tex
further cover letter corrections, passing over to Seb

The pairwise correlations in the initial set of features appears in Fig.~\ref{fig:feature-corrs-initial}.
By looking at absolute values, three subsets of highly correlated features can be easily identified:
(a) number of letters, phonemes, and syllables with pairwise correlations greater than .75;
(b) orthographic and phonological neighborhood densities, with a correlation of .8;
(c) age of acquisition, betweenness, degree, and pagerank centralities, with absolute pairwise correlations at .41, .6, .59, .63, .61 and .85.
Applying a feature agglomeration algorithm targeted at 6 groups refined this observation by producing identical (a) and (b) groups, a (c) group without betweenness centrality which was instead assigned to a group (d) with clustering coefficient, and the remaining features (frequency and number of synonyms) as singletons.\footnote{
\newtext{Agglomerating into less than 6 groups merged groups (a) and (b), which we excluded to keep neighborhood densities in their own group;
agglomerating into more than 6 groups separated age of acquisition from group (c), which we excluded given its high correlation values to the rest of group (c). 
We used scikit-learn's FeatureAgglomeration class for this procedure~\citep{pedregosa_scikit-learn:_2011}.}
}

Since our data is about written transformations, number of letters and orthographic neighborhood density are the natural representatives of groups (a) and (b) respectively.
Given the importance of age of acquisition in the lexical feature literature, we chose it to represent group (c).
Finally we used clustering coefficient to represent group (d) since it has already been used in previous studies.
The final set of features we will discuss in the rest of the paper, as well as their cross-correlations, can be seen in Fig.~\ref{fig:feature-corrs-filtered}.% (the analysis on the complete set of features can be found in the appendix).
\footnote{
Note that feature values stem from different data sets which do not always encode the same words.
Indeed, we have data on frequency for about \newtext{33.5k} words, on age of acquisition for 30.1k words, on clustering coefficient for 5.7k words, number of synonyms 111.2k, and \newtext{orthographic density 17.8k words}.
Quite often then, not all features are available for all words in our data set;
however this is not problematic since the analysis is done on a per-feature basis, and not all words need be encoded in all features.}

>>>>

The pairwise correlations in the initial set of features appears in Fig.~\ref{fig:feature-corrs-initial}.
By looking at absolute values, three subsets of highly correlated features can be easily identified:
(a) number of letters, phonemes, and syllables with pairwise correlations greater than .75;
(b) orthographic and phonological neighborhood densities, with a correlation of .8;
(c) age of acquisition, betweenness, degree, and pagerank centralities, with absolute pairwise correlations at .41, .6, .59, .63, .61 and .85.
Applying a feature agglomeration algorithm targeted at 6 groups refined this observation by producing identical (a) and (b) groups, a (c) group without betweenness centrality which was instead assigned to a group (d) with clustering coefficient, and the remaining features (frequency and number of synonyms) as singletons.\footnote{
\newtext{Agglomerating into less than 6 groups merged groups (a) and (b), which we excluded to keep neighborhood densities in their own group;
agglomerating into more than 6 groups separated age of acquisition from group (c), which we excluded given its high correlation values to the rest of group (c). 
We used scikit-learn's FeatureAgglomeration class for this procedure~\citep{pedregosa_scikit-learn:_2011}.}
}
\end{new}

\begin{new}
Since our data is about written transformations, number of letters and orthographic neighborhood density are the natural representatives of groups (a) and (b) respectively.
Given the importance of age of acquisition in the lexical feature literature, we chose it to represent group (c).
Finally we used clustering coefficient to represent group (d) since it has already been used in previous studies.
The final set of features we will discuss in the rest of the paper, as well as their cross-correlations, can be seen in Fig.~\ref{fig:feature-corrs-filtered}.% (the analysis on the complete set of features can be found in the appendix).
\footnote{
Note that feature values stem from different data sets which do not always encode the same words.
Indeed, we have data on frequency for about \newtext{33.5k} words, on age of acquisition for 30.1k words, on clustering coefficient for 5.7k words, number of synonyms 111.2k, and \newtext{orthographic density 17.8k words}.
Quite often then, not all features are available for all words in our data set;
however this is not problematic since the analysis is done on a per-feature basis, and not all words need be encoded in all features.}
\end{new}
